---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

# revise

<!-- badges: start -->
[![R-CMD-check](https://github.com/conig/revise/workflows/R-CMD-check/badge.svg)](https://github.com/conig/revise/actions)
<!-- badges: end -->

The goal of revise is to support authors in responding to revise and resubmit requests. These functions are designed to work with [crsh/papaja](https://github.com/crsh/papaja).

## Installation

You can install the development version of {revise} from [GitHub](https://github.com/conig/revise) with:

``` r
# install.packages("remotes")
remotes::install_github("conig/revise")
```
# Starting a revision document

You can use rmd or docx files with revise. To load either, simply call revise::read_manuscript("your_file.rmd")

For example. Here is an example docx where content has been tagged with comment boxes. E.g, Revise::hard

```{r}
docx_path <- system.file("examples/word_test.docx", package = "revise")

man <- read_manuscript(docx_path)
man
```

We can see all tagged sections by running

```{r}
names(man$sections)
```

Then we can retrieve using a section name

```{r}
revision <- get_revision("hard", man)
revision
```

This content can then be put directly into a response document using single backticks.

# Tagging sections in a manuscript for extraction

There are two methods to tag sections in manuscript for extraction. We support using id attributes in html spans:

```{md}
<span id="multi-line">
This is a multi-line section of text.

We have tagged it with the section name "multi-line".
</span>
```
We also support a markdown variant for quick inline tagging:

```{md}
[This is a single line of text we have tagged using markdown.]{#single-line-example}
```

In both cases pandoc ignores these tags when rendering the document, but they can be used by revise to extract content.



